fdcoexist

### 2018-08-21 paper_simulations.Rmd
:hammer: tidied up code to make synthetic :art: plot

```{r synthetic_plot}

list_df <- list("no_compet_no_cor_df" = no_compet_no_cor_df,
                "no_compet_low_cor_df" = no_compet_low_cor_df,
                "no_compet_high_cor_df" = no_compet_high_cor_df,
                "compet_no_cor_df" = compet_no_cor_df,
                "compet_low_cor_df" = compet_low_cor_df,
                "compet_high_cor_df" = compet_high_cor_df)
list_df <- mapply(cbind, list_df, "var_df" = names(list_df),
                  SIMPLIFY = FALSE)
list_df <- lapply(list_df, function(x) data.frame(x, type = "constant"))

list_var_df <- list("no_compet_no_cor_var_df" = no_compet_no_cor_var_df,
                    "no_compet_low_cor_var_df" = no_compet_low_cor_var_df,
                    "no_compet_high_cor_var_df" = no_compet_high_cor_var_df,
                    "compet_no_cor_var_df" = compet_no_cor_var_df,
                    "compet_low_cor_var_df" = compet_low_cor_var_df,
                    "compet_high_cor_var_df" = compet_high_cor_var_df)
list_var_df <- mapply(cbind, list_var_df, "var_df" = names(list_var_df),
                      SIMPLIFY = FALSE)
list_var_df <- lapply(list_var_df, function(x) data.frame(x, type = "varying"))

all_list <- c(list_df, list_var_df)

all_df <- as.data.frame(bind_rows(all_list))

# List of weighted linear regressions
trait2_w_lm = all_df %>%
    group_by(var_df, scenario) %>%
    do(model = lm(trait2 ~ patch_optim, data = ., weights = N))

list_lm_df <- trait2_w_lm[[1]]
list_lm_scenario <- trait2_w_lm[[2]]

trait2_w_lm <- lapply(trait2_w_lm$model, summary)

synth_plot <- data.frame(df = list_lm_df,
                         scenario = list_lm_scenario,
                         r2 = unlist(lapply(trait2_w_lm,
                                            function(x) x$r.squared)))

synth_plot$df <- as.factor(synth_plot$df)
synth_plot$df <- factor(synth_plot$df,
                        levels(synth_plot$df)[c(6:1)])
synth_plot$compet <- ifelse(grepl("no_compet", synth_plot$df), "No", "Competition")
synth_plot$type <- ifelse(grepl("_var_", synth_plot$df), "Varying", "Constant")

print(ggplot(synth_plot, aes(as.factor(df), r2)) +
          geom_point(aes(shape = as.factor(scenario),
                         fill = as.factor(compet)),
                     color = "black", size = 4) +
          scale_fill_manual("Competition", values = c(No = "#a50026",
                                                      Competition = "#313695")) +
          scale_shape_manual("Scenario", values = c(RA100100 = 21, RA2575 = 22,
                                                    RA5050 = 23, RA7525 = 24)) +
          facet_wrap(~ type) +
          labs(subtitle = "R2 for the weighted linear regression between trait2 and environment",
               x = "Scenario",
               y = expression("R"^2)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          guides(color = FALSE,
                 fill = guide_legend(override.aes = list(shape = 21,
                                                         size = 4))))

```

>>>>

```{r synthetic_plot}
list_df <- list("no_compet_no_cor_df" = no_compet_no_cor_df,
                "no_compet_low_cor_df" = no_compet_low_cor_df,
                "no_compet_high_cor_df" = no_compet_high_cor_df,
                "compet_no_cor_df" = compet_no_cor_df,
                "compet_low_cor_df" = compet_low_cor_df,
                "compet_high_cor_df" = compet_high_cor_df) %>%
    # Merge as a single data.frame
    bind_rows(.id = "original_name") %>%
    # Extract comptetition and correlation status
    mutate(original_name = gsub("_df", "", original_name)) %>%
    extract(original_name, c("compet_status", "cor_level"),
            "([:alpha:]*_?compet)_(.*)")

list_var_df <- list("no_compet_no_cor_var_df" = no_compet_no_cor_var_df,
                    "no_compet_low_cor_var_df" = no_compet_low_cor_var_df,
                    "no_compet_high_cor_var_df" = no_compet_high_cor_var_df,
                    "compet_no_cor_var_df" = compet_no_cor_var_df,
                    "compet_low_cor_var_df" = compet_low_cor_var_df,
                    "compet_high_cor_var_df" = compet_high_cor_var_df) %>%
    # Merge as a single data.frame
    bind_rows(.id = "original_name") %>%
    # Extract comptetition and correlation status
    mutate(original_name = gsub("_var_df", "", original_name)) %>%
    extract(original_name, c("compet_status", "cor_level"),
            "([:alpha:]*_?compet)_(.*)")

# Combine data.frame from different environment length
all_df <- list(constant = list_df, varying = list_var_df) %>%
    bind_rows(.id = "env_width")

# Compute linear models for CWM <-> environment relationship
mod_df <- all_df %>%
    group_by(env_width, compet_status, cor_level, scenario, patch) %>%
    summarise(patch_optim = unique(patch_optim), trait2_cwm = sum(trait2_cwm)) %>%
    nest() %>%
    mutate(mod_cwm_env = map(data, ~lm(trait2_cwm ~ patch_optim, data = .x)),
           mod_glance = map(mod_cwm_env, broom::glance)) %>%
    unnest(mod_glance)

# R2 plot
plot_r2_cwm_env = ggplot(mod_df, aes(scenario, r.squared)) +
    geom_point(aes(fill = fct_rev(cor_level)),
               size = 4, position = position_dodge(width = 0.7),
               shape = 21) +
    facet_grid(rows = vars(compet_status), cols = vars(env_width),
               labeller =
                   labeller(compet_status = c(compet = "Competition",
                                              no_compet = "No Competition"),
                            env_width     = c(constant = "Constant\nEnv. Filter Strength",
                                               varying  = "Varying\nEnv. Filter Strength"))) +
    ylim(0, NA) +
    scale_fill_viridis_d("Trait\nCorrelations",
                         labels = c(no_cor   = "r = 0",
                                    low_cor  = "r = 0.3",
                                    high_cor = "r = 0.7")) +
    guides(color = FALSE,
           fill = guide_legend(override.aes = list(shape = 21,
                                                   size = 4))) +
    labs(subtitle = "R2 of trait2 CWM ~ environment",
         x = "Scenario",
         y = expression("R"^2)) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "top")

plot_r2_cwm_env
```
